Disturbance-aware minimum-time planning strategies for motorsport vehicles with probabilistic safety certificates

### 2025-06-03 performance_comparison.tex
[MM] tmp for Martino

As expected, the two configurations with the robustified friction limit constraint (red and blue lines) never reach a value of 1, due to the presence of the back-off term, which enforces a safety margin from the friction limit.

>>>>

As expected, the two configurations with the robustified friction limit constraint (red and blue lines) never reach a value of 1, due to the presence of the back-off term, which enforces a safety margin from the friction limit. 
From this plot, it can be observed that the configurations with the robustified track limit constraint (green and blue lines) follow significantly different trajectories compared to the nominal solution, resulting in distinct ground force demands. This behavior is noticeable in turn 1 and even more clearly in turn 2. Specifically, these two configurations begin to experience high axle loads approximately 12\,m before the nominal trajectory and sustain them for an additional 4.6\,m (TLC, green line) and 9.2\,m (TLC+FLC, blue line) beyond the nominal reference.
